A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-29 bioc-workflow.tex
add final sections

\section{Introduction}\label{introduction}

@@

The main package to analyse protein localisation data is
\texttt{r Biocpkg("pRoloc")}, which offers a set of dedicated functions
for the analysis of such data.
\emph{\href{http://bioconductor.org/packages/pRoloc}{pRoloc}} itself
relies on \texttt{r Biocpkg("MSnbase")} to manipulate and process
quantitative proteomics data. Many other packages are used by
\emph{\href{http://bioconductor.org/packages/pRoloc}{pRoloc}} for
clustering, classification and visualisation.

In this workflow, we will describe how to prepare the spatial proteomics
data starting from a spreadsheet containing quantitative mass
spectrometry data. We will focus on a recent pluripotent mouse embryonic
stem cells experiment {[}@hyper{]}. Additional annotated and
pre-formatted datasets from various species are readily available in the
\emph{\href{http://bioconductor.org/packages/pRolocdata}{pRolocdata}}
package.

Installation of Bioconductor package is documented in details on the
\href{http://bioconductor.org/install/\#install-bioconductor-packages}{Bioconductor
installation help page}. This procedure is also applicable to any
packages, from \href{https://cran.r-project.org/}{CRAN} as well as
GitHub. Once a package has been installed, it needs to be loaded for its
functionality to become available in the R session; this is done with
the \texttt{library} function e.g. to load the
\emph{\href{http://bioconductor.org/packages/pRoloc}{pRoloc}} one would
type \texttt{library("pRoloc")} after installation.

If you have questions about this workflow in particular, or about other
Bioconductor packages in general, they are best asked on the
\href{https://support.bioconductor.org/}{Bioconductor support site}
following the
\href{http://www.bioconductor.org/help/support/posting-guide/}{posting
guidelines}. Questions can be tagged with specific package names or
keywords. For more general information about mass spectrometry and
proteomics, the readers are invited to read the
\emph{\href{http://bioconductor.org/packages/RforProteomics}{RforProteomics}}
package vignettes and associated papers {[}@Gatto:2014;@Gatto2015{]}.

\section{Reading and processing spatial proteomics
data}\label{reading-and-processing-spatial-proteomics-data}

\subsection{The use-case: predicting sub-cellular localisation in
pluripotent embryonic mouse stem
cells}\label{the-use-case-predicting-sub-cellular-localisation-in-pluripotent-embryonic-mouse-stem-cells}

As a use-case, we analyse a recent high-throughput spatial proteomics
dataset from pluripotent mouse embryonic stem cells (E14TG2a)
{[}@hyper{]}. The data was generated using hyperplexed LOPIT
(hyperLOPIT), a state-of-the-art method relying on improved sub-cellular
fractionation and more accurate quantitation, leading to more reliable
classification of protein localisation across the whole sub-cellular
space. The method uses an elaborate sub-cellular fractionation scheme,
enabled by the use of Tandem Mass Tag (TMT) {[}Thompson:2003{]} 10-plex
and application of the MS data acquisition technique named synchronous
precursor selection MS\textsuperscript{3} (SPS-MS\textsuperscript{3})
{[}@McAlister:2014{]}, for TMT quantification with high accuracy and
precision. Three biological replicates were generated from the E14TG2a
experiment, the first was to target low density fractions and the second
and third were to emphasis separation of the denser organelles. The
intersect of replicates 1 and 2 was treated as a 20-plex dataset for the
analysis. As discussed in the manuscript {[}@hyper{]} as it has been
shown that combining replicates across from different gradients can
increase spatial resolution {[}@Trotter:2010{]}. The combination of
replicates resulted in 5032 proteins common in both experiments.

These, as well as many other data are directly available as properly
structured and annotated computational object from the
\emph{\href{http://bioconductor.org/packages/pRolocdata}{pRolocdata}}
experiment package. In this workflow, we will start with a description
of how to generate these ad hoc objects starting from an arbitrary
spreadsheets, as produced by many popular third-party applications.

While we focus here on a LOPIT-type dataset, these analyses are relevant
for any quantitative spatial proteomics data, irrespective of the
fractionation or quantitation (i.e.~labelled or label-free) methods.

\subsection{The infrastructure:
\emph{\href{http://bioconductor.org/packages/pRoloc}{pRoloc}} and
\emph{\href{http://bioconductor.org/packages/MSnbase}{MSnbase}} in
Bioconductor}\label{the-infrastructure-proloc-and-msnbase-in-bioconductor}

To make use of the full functionality of the
\emph{\href{http://bioconductor.org/packages/pRoloc}{pRoloc}} software
one needs to import their data into R and prepare them as an
\texttt{MSnSet}. The \texttt{MSnSet} is a dedicated data structure for
the efficient manipulation and processing of mass spectrometry and
proteomics data in R. Figure 1 illustrates a simplified view of the
\texttt{MSnSet} structure; there exists 3 key sub-parts (termed slots)
to such a data object: (1) the \texttt{exprs} slot for storing the
quantitation data, (2) the \texttt{fData} slot for storing the feature
meta-data, and finally (3) the \texttt{pData} slot for storing the
sample meta-data.

\begin{figure}[htbp]
\centering
\includegraphics{./Figures/msnset.png}
\caption{Simplified representation of the \texttt{MSnSet} data structure
(reproduced with permission from the
\emph{\href{http://bioconductor.org/packages/MSnbase}{MSnbase}}
vignette)}
\end{figure}

\subsection{Importing data}\label{importing-data}

There are a number of ways to import quantitation data and create an
\texttt{MSnSet} instance. All methods are described in the
\emph{\href{http://bioconductor.org/packages/MSnbase}{MSnbase}}
\href{http://bioconductor.org/packages/release/bioc/vignettes/MSnbase/inst/doc/MSnbase-io.pdf}{input/output
capabilities vignette}. One suggested simple method is to use the
function \texttt{readMSnSet2} in
\emph{\href{http://bioconductor.org/packages/MSnbase}{MSnbase}}. The
function takes a single spreadsheet as input and extracts the columns
containing the quantitation data, as identified by the argument
\texttt{ecol}, to create the expression data, while the other columns in
the spreadsheet are appended to the feature meta-data slot. By example,
in the code chunk below we read in the \texttt{csv} spreadsheet
containing the quantitation data from the intersect of replicates 1 and
2 of the mouse map {[}@hyper{]}, using the \texttt{readMSnSet2}
function. The data is as available online with the manuscript (see tab 2
of the \texttt{xlsx} supplementary data set 1 in {[}@hyper{]}, which
should be exported as a text-based spreadsheet). It is also available as
a \texttt{csv} in the Bioconductor \texttt{r Biocexptpkg("pRolocdata")}
data package.

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(}\StringTok{"MSnbase"}\NormalTok{)}
\NormalTok{extdatadir <-}\StringTok{ }\KeywordTok{system.file}\NormalTok{(}\StringTok{"extdata"}\NormalTok{, }\DataTypeTok{package =} \StringTok{"pRolocdata"}\NormalTok{)}
\NormalTok{csvfile <-}\StringTok{ }\KeywordTok{dir}\NormalTok{(extdatadir, }\DataTypeTok{full.names =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{pattern =} \StringTok{"hyperLOPIT-SIData-ms3-rep12-intersect.csv"}\NormalTok{)}
\KeywordTok{basename}\NormalTok{(csvfile)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "hyperLOPIT-SIData-ms3-rep12-intersect.csv.gz"
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{getEcols}\NormalTok{(csvfile, }\DataTypeTok{split =} \StringTok{","}\NormalTok{, }\DataTypeTok{n =} \DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  [1] ""                                 
##  [2] ""                                 
##  [3] ""                                 
##  [4] "Experiment 1"                     
##  [5] "Experiment 2"                     
##  [6] "Experiment 1"                     
##  [7] "Experiment 2"                     
##  [8] "126"                              
##  [9] "127N"                             
## [10] "127C"                             
## [11] "128N"                             
## [12] "128C"                             
## [13] "129N"                             
## [14] "129C"                             
## [15] "130N"                             
## [16] "130C"                             
## [17] "131"                              
## [18] "126"                              
## [19] "127N"                             
## [20] "127C"                             
## [21] "128N"                             
## [22] "128C"                             
## [23] "129N"                             
## [24] "129C"                             
## [25] "130N"                             
## [26] "130C"                             
## [27] "131"                              
## [28] "phenoDisco Input"                 
## [29] "phenoDisco Output"                
## [30] "Curated phenoDisco Output"        
## [31] "SVM marker set"                   
## [32] "SVM classification"               
## [33] "SVM score"                        
## [34] "SVM classification (top quartile)"
## [35] "Final Localization Assignment"    
## [36] "First localization evidence?"     
## [37] "Curated Organelles"               
## [38] "Cytoskeletal Components"          
## [39] "Trafficking Proteins"             
## [40] "Protein Complexes"                
## [41] "Signaling Cascades"               
## [42] "Oct4 Interactome"                 
## [43] "Nanog Interactome"                
## [44] "Sox2 Interactome"                 
## [45] "Cell Surface Proteins"
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{hl <-}\StringTok{ }\KeywordTok{readMSnSet2}\NormalTok{(csvfile, }\DataTypeTok{ecol =} \DecValTok{8}\NormalTok{:}\DecValTok{27}\NormalTok{, }\DataTypeTok{fnames =} \DecValTok{1}\NormalTok{, }\DataTypeTok{skip =} \DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{hl}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData: none
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: X X.1 ... Cell.Surface.Proteins (25 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
##  MSnbase version: 1.99.2
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{exprs}\NormalTok{(hl)[}\DecValTok{1}\NormalTok{:}\DecValTok{5}\NormalTok{, ]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##           X126 X127N X127C X128N X128C X129N X129C X130N X130C  X131
## Q9JHU4   0.028 0.034 0.024 0.014 0.026 0.045 0.107 0.341 0.059 0.321
## Q9QXS1-3 0.039 0.134 0.095 0.053 0.084 0.121 0.107 0.128 0.122 0.117
## Q9ERU9   0.021 0.013 0.014 0.009 0.024 0.054 0.116 0.257 0.209 0.284
## P26039   0.120 0.255 0.148 0.091 0.135 0.095 0.041 0.057 0.014 0.043
## Q8BTM8   0.055 0.139 0.078 0.050 0.077 0.098 0.093 0.171 0.079 0.160
##          X126.1 X127N.1 X127C.1 X128N.1 X128C.1 X129N.1 X129C.1 X130N.1
## Q9JHU4    0.037   0.064   0.058   0.059   0.067   0.078   0.140   0.208
## Q9QXS1-3  0.033   0.073   0.074   0.062   0.081   0.142   0.190   0.069
## Q9ERU9    0.026   0.017   0.023   0.029   0.039   0.071   0.105   0.171
## P26039    0.111   0.181   0.141   0.144   0.152   0.119   0.075   0.028
## Q8BTM8    0.062   0.108   0.091   0.086   0.099   0.111   0.117   0.095
##          X130C.1 X131.1
## Q9JHU4     0.141  0.147
## Q9QXS1-3   0.151  0.125
## Q9ERU9     0.304  0.215
## P26039     0.017  0.033
## Q8BTM8     0.144  0.087
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{exprs}\NormalTok{(hl)[}\KeywordTok{c}\NormalTok{(}\StringTok{"Q9ERU9"}\NormalTok{, }\StringTok{"Q9Z2R6"}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\StringTok{"X126"}\NormalTok{, }\StringTok{"X131.1"}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##         X126 X131.1
## Q9ERU9 0.021  0.215
## Q9Z2R6 0.563  0.000
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fvarLabels}\NormalTok{(hl)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  [1] "X"                                
##  [2] "X.1"                              
##  [3] "X.2"                              
##  [4] "Experiment.1"                     
##  [5] "Experiment.2"                     
##  [6] "Experiment.1.1"                   
##  [7] "Experiment.2.1"                   
##  [8] "phenoDisco.Input"                 
##  [9] "phenoDisco.Output"                
## [10] "Curated.phenoDisco.Output"        
## [11] "SVM.marker.set"                   
## [12] "SVM.classification"               
## [13] "SVM.score"                        
## [14] "SVM.classification..top.quartile."
## [15] "Final.Localization.Assignment"    
## [16] "First.localization.evidence."     
## [17] "Curated.Organelles"               
## [18] "Cytoskeletal.Components"          
## [19] "Trafficking.Proteins"             
## [20] "Protein.Complexes"                
## [21] "Signaling.Cascades"               
## [22] "Oct4.Interactome"                 
## [23] "Nanog.Interactome"                
## [24] "Sox2.Interactome"                 
## [25] "Cell.Surface.Proteins"
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{fvarLabels}\NormalTok{(hl)[}\DecValTok{1}\NormalTok{:}\DecValTok{3}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"uniprot.accession"}\NormalTok{, }\StringTok{"uniprot.id"}\NormalTok{, }\StringTok{"description"}\NormalTok{)}
\KeywordTok{fvarLabels}\NormalTok{(hl)[}\DecValTok{4}\NormalTok{:}\DecValTok{6}\NormalTok{] <-}\StringTok{ }\KeywordTok{paste0}\NormalTok{(}\StringTok{"peptides.expt"}\NormalTok{, }\DecValTok{1}\NormalTok{:}\DecValTok{3}\NormalTok{)}
\KeywordTok{fData}\NormalTok{(hl)[}\DecValTok{1}\NormalTok{:}\DecValTok{4}\NormalTok{, }\DecValTok{1}\NormalTok{:}\DecValTok{6}\NormalTok{]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##          uniprot.accession  uniprot.id
## Q9JHU4              Q9JHU4 DYHC1_MOUSE
## Q9QXS1-3          Q9QXS1-3  PLEC_MOUSE
## Q9ERU9              Q9ERU9  RBP2_MOUSE
## P26039              P26039  TLN1_MOUSE
##                                                                                                                                 description
## Q9JHU4                                              Cytoplasmic dynein 1 heavy chain 1 OS=Mus musculus GN=Dync1h1 PE=1 SV=2 - [DYHC1_MOUSE]
## Q9QXS1-3 Isoform PLEC-1 of Plectin OS=Mus musculus GN=Plec - [PLEC_MOUSE]|Isoform PLEC-1A of Plectin OS=Mus musculus GN=Plec - [PLEC_MOUSE]
## Q9ERU9                                                     E3 SUMO-protein ligase RanBP2 OS=Mus musculus GN=Ranbp2 PE=1 SV=2 - [RBP2_MOUSE]
## P26039                                                                             Talin-1 OS=Mus musculus GN=Tln1 PE=1 SV=2 - [TLN1_MOUSE]
##          peptides.expt1 peptides.expt2 peptides.expt3
## Q9JHU4              175            166            322
## Q9QXS1-3            123            150            174
## Q9ERU9              101             90            181
## P26039              101             94            167
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{pData}\NormalTok{(hl)$Replicate <-}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{:}\DecValTok{2}\NormalTok{, }\DataTypeTok{each =} \DecValTok{10}\NormalTok{)}
\KeywordTok{pData}\NormalTok{(hl)$Tag <-}\StringTok{ }\KeywordTok{sub}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{.1$"}\NormalTok{, }\StringTok{""}\NormalTok{, }\KeywordTok{sub}\NormalTok{(}\StringTok{"^X"}\NormalTok{, }\StringTok{""}\NormalTok{, }\KeywordTok{sampleNames}\NormalTok{(hl)))}
\KeywordTok{pData}\NormalTok{(hl)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##         Replicate  Tag
## X126            1  126
## X127N           1 127N
## X127C           1 127C
## X128N           1 128N
## X128C           1 128C
## X129N           1 129N
## X129C           1 129C
## X130N           1 130N
## X130C           1 130C
## X131            1  131
## X126.1          2  126
## X127N.1         2 127N
## X127C.1         2 127C
## X128N.1         2 128N
## X128C.1         2 128C
## X129N.1         2 129N
## X129C.1         2 129C
## X130N.1         2 130N
## X130C.1         2 130C
## X131.1          2  131
\end{verbatim}

>>>>

\section*{Introduction}

@@

The main package to analyse protein localisation data is
\Biocpkg{pRoloc}, which offers a set of dedicated functions for the
analysis of such data. \Biocpkg{pRoloc} itself relies on
\Biocpkg{MSnbase} to manipulate and process quantitative
proteomics data. Many other packages are used by \Biocpkg{pRoloc}
for clustering, classification and visualisation.

In this workflow, we will describe how to prepare the spatial
proteomics data starting from a spreadsheet containing quantitative
mass spectrometry data. We will focus on a recent pluripotent mouse
embryonic stem cells experiment \cite{hyper}. Additional annotated and
pre-formatted datasets from various species are readily available in
the \Biocexptpkg{pRolocdata} package.

Installation of Bioconductor package is documented in details on the
\href{http://bioconductor.org/install/#install-bioconductor-packages}{Bioconductor
  installation help page}. This procedure is also applicable to any
packages, from \href{https://cran.r-project.org/}{CRAN} as well as
GitHub. Once a package has been installed, it needs to be loaded for
its functionality to become available in the R session; this is done
with the \texttt{library} function e.g.  to load the
\Biocpkg{pRoloc} one would type \texttt{library("pRoloc")}
after installation.

If you have questions about this workflow in particular, or about
other Bioconductor packages in general, they are best asked on the
\href{https://support.bioconductor.org/}{Bioconductor support site}
following the
\href{http://www.bioconductor.org/help/support/posting-guide/}{posting
  guidelines}. Questions can be tagged with specific package names or
keywords. For more general information about mass spectrometry and
proteomics, the readers are invited to read the
\Biocexptpkg{"RforProteomics"} package vignettes and associated
papers \cite{Gatto:2014,Gatto:2015}.

\section*{Reading and processing spatial proteomics data}

\subsection*{The use-case: predicting sub-cellular localisation in pluripotent embryonic mouse stem cells}

As a use-case, we analyse a recent high-throughput spatial proteomics
dataset from pluripotent mouse embryonic stem cells (E14TG2a)
\cite{hyper}. The data was generated using hyperplexed LOPIT
(hyperLOPIT), a state-of-the-art method relying on improved
sub-cellular fractionation and more accurate quantitation, leading to
more reliable classification of protein localisation across the whole
sub-cellular space. The method uses an elaborate sub-cellular
fractionation scheme, enabled by the use of Tandem Mass Tag (TMT)
\cite{Thompson:2003} 10-plex and application of the MS data
acquisition technique named synchronous precursor selection MS$^3$
(SPS-MS$^3$) \cite{McAlister:2014}, for TMT quantification with high
accuracy and precision. Three biological replicates were generated
from the E14TG2a experiment, the first was to target low density
fractions and the second and third were to emphasis separation of the
denser organelles.  The intersect of replicates 1 and 2 was treated as
a 20-plex dataset for the analysis.  As discussed in the manuscript
\cite{hyper} as it has been shown that combining replicates across
from different gradients can increase spatial resolution
\cite{Trotter:2010}. The combination of replicates resulted in 5032
proteins common in both experiments.

These, as well as many other data are directly available as properly
structured and annotated computational object from the 
\Biocexptpkg{pRolocdata} experiment package. In this workflow, we
will start with a description of how to generate these ad hoc objects
starting from an arbitrary spreadsheets, as produced by many popular
third-party applications.

While we focus here on a LOPIT-type dataset, these analyses are
relevant for any quantitative spatial proteomics data, irrespective of
the fractionation or quantitation (i.e. labelled or label-free)
methods.

\subsection*{The infrastructure: \texttt{pRoloc} and \texttt{MSnbase} packages}

To make use of the full functionality of the \Biocpkg{pRoloc}
software one needs to import their data into R and prepare them as an
\texttt{MSnSet}. The \texttt{MSnSet} is a dedicated data structure for the efficient
manipulation and processing of mass spectrometry and proteomics data
in R. Figure 1 illustrates a simplified view of the \texttt{MSnSet}
structure; there exists 3 key sub-parts (termed slots) to such a data
object: (1) the \texttt{exprs} slot for storing the quantitation data, (2)
the \texttt{fData} slot for storing the feature meta-data, and finally (3)
the \texttt{pData} slot for storing the sample meta-data.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=.5\textwidth]{./Figures/msnset.png}
  \caption{Simplified representation of the \texttt{MSnSet} data
    structure (reproduced with permission from the \Biocpkg{MSnbase}
    vignette)}
  \label{fig:msnset}
\end{figure}

\subsection*{Importing data}

There are a number of ways to import quantitation data and create an
\texttt{MSnSet} instance. All methods are described in the
\Biocpkg{MSnbase}
\href{http://bioconductor.org/packages/release/bioc/vignettes/MSnbase/inst/doc/MSnbase-io.pdf}{input/output
  capabilities vignette}. One suggested simple method is to use the
function \texttt{readMSnSet2} in \Biocpkg{MSnbase}. The function
takes a single spreadsheet as input and extracts the columns
containing the quantitation data, as identified by the argument
\texttt{ecol}, to create the expression data, while the other columns
in the spreadsheet are appended to the feature meta-data slot.  By
example, in the code chunk below we read in the \texttt{csv}
spreadsheet containing the quantitation data from the intersect of
replicates 1 and 2 of the mouse map \cite{hyper}, using the
\texttt{readMSnSet2} function. The data is as available online with
the manuscript (see tab 2 of the \texttt{xlsx} supplementary data set
1 in \cite{hyper}, which should be exported as a text-based
spreadsheet). It is also available as a \texttt{csv} in the
Bioconductor \Biocexptpkg{pRolocdata} data package.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(}\hlstr{"MSnbase"}\hlstd{)}
\hlstd{extdatadir} \hlkwb{<-} \hlkwd{system.file}\hlstd{(}\hlstr{"extdata"}\hlstd{,} \hlkwc{package} \hlstd{=} \hlstr{"pRolocdata"}\hlstd{)}
\hlstd{csvfile} \hlkwb{<-} \hlkwd{dir}\hlstd{(extdatadir,} \hlkwc{full.names} \hlstd{=} \hlnum{TRUE}\hlstd{,}
          \hlkwc{pattern} \hlstd{=} \hlstr{"hyperLOPIT-SIData-ms3-rep12-intersect.csv"}\hlstd{)}
\hlkwd{basename}\hlstd{(csvfile)}
\end{alltt}
\begin{verbatim}
## [1] "hyperLOPIT-SIData-ms3-rep12-intersect.csv.gz"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{getEcols}\hlstd{(csvfile,} \hlkwc{split} \hlstd{=} \hlstr{","}\hlstd{,} \hlkwc{n} \hlstd{=} \hlnum{2}\hlstd{)}
\end{alltt}
\begin{verbatim}
##  [1] ""                                 
##  [2] ""                                 
##  [3] ""                                 
##  [4] "Experiment 1"                     
##  [5] "Experiment 2"                     
##  [6] "Experiment 1"                     
##  [7] "Experiment 2"                     
##  [8] "126"                              
##  [9] "127N"                             
## [10] "127C"                             
## [11] "128N"                             
## [12] "128C"                             
## [13] "129N"                             
## [14] "129C"                             
## [15] "130N"                             
## [16] "130C"                             
## [17] "131"                              
## [18] "126"                              
## [19] "127N"                             
## [20] "127C"                             
## [21] "128N"                             
## [22] "128C"                             
## [23] "129N"                             
## [24] "129C"                             
## [25] "130N"                             
## [26] "130C"                             
## [27] "131"                              
## [28] "phenoDisco Input"                 
## [29] "phenoDisco Output"                
## [30] "Curated phenoDisco Output"        
## [31] "SVM marker set"                   
## [32] "SVM classification"               
## [33] "SVM score"                        
## [34] "SVM classification (top quartile)"
## [35] "Final Localization Assignment"    
## [36] "First localization evidence?"     
## [37] "Curated Organelles"               
## [38] "Cytoskeletal Components"          
## [39] "Trafficking Proteins"             
## [40] "Protein Complexes"                
## [41] "Signaling Cascades"               
## [42] "Oct4 Interactome"                 
## [43] "Nanog Interactome"                
## [44] "Sox2 Interactome"                 
## [45] "Cell Surface Proteins"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{readMSnSet2}\hlstd{(csvfile,} \hlkwc{ecol} \hlstd{=} \hlnum{8}\hlopt{:}\hlnum{27}\hlstd{,} \hlkwc{fnames} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{skip} \hlstd{=} \hlnum{1}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData: none
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: X X.1 ... Cell.Surface.Proteins (25 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
##  MSnbase version: 1.99.2
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{exprs}\hlstd{(hl)[}\hlnum{1}\hlopt{:}\hlnum{5}\hlstd{, ]}
\end{alltt}
\begin{verbatim}
##           X126 X127N X127C X128N X128C X129N X129C X130N X130C  X131
## Q9JHU4   0.028 0.034 0.024 0.014 0.026 0.045 0.107 0.341 0.059 0.321
## Q9QXS1-3 0.039 0.134 0.095 0.053 0.084 0.121 0.107 0.128 0.122 0.117
## Q9ERU9   0.021 0.013 0.014 0.009 0.024 0.054 0.116 0.257 0.209 0.284
## P26039   0.120 0.255 0.148 0.091 0.135 0.095 0.041 0.057 0.014 0.043
## Q8BTM8   0.055 0.139 0.078 0.050 0.077 0.098 0.093 0.171 0.079 0.160
##          X126.1 X127N.1 X127C.1 X128N.1 X128C.1 X129N.1 X129C.1 X130N.1
## Q9JHU4    0.037   0.064   0.058   0.059   0.067   0.078   0.140   0.208
## Q9QXS1-3  0.033   0.073   0.074   0.062   0.081   0.142   0.190   0.069
## Q9ERU9    0.026   0.017   0.023   0.029   0.039   0.071   0.105   0.171
## P26039    0.111   0.181   0.141   0.144   0.152   0.119   0.075   0.028
## Q8BTM8    0.062   0.108   0.091   0.086   0.099   0.111   0.117   0.095
##          X130C.1 X131.1
## Q9JHU4     0.141  0.147
## Q9QXS1-3   0.151  0.125
## Q9ERU9     0.304  0.215
## P26039     0.017  0.033
## Q8BTM8     0.144  0.087
\end{verbatim}
\begin{alltt}
\hlkwd{exprs}\hlstd{(hl)[}\hlkwd{c}\hlstd{(}\hlstr{"Q9ERU9"}\hlstd{,} \hlstr{"Q9Z2R6"}\hlstd{),} \hlkwd{c}\hlstd{(}\hlstr{"X126"}\hlstd{,} \hlstr{"X131.1"}\hlstd{)]}
\end{alltt}
\begin{verbatim}
##         X126 X131.1
## Q9ERU9 0.021  0.215
## Q9Z2R6 0.563  0.000
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hl)}
\end{alltt}
\begin{verbatim}
##  [1] "X"                                
##  [2] "X.1"                              
##  [3] "X.2"                              
##  [4] "Experiment.1"                     
##  [5] "Experiment.2"                     
##  [6] "Experiment.1.1"                   
##  [7] "Experiment.2.1"                   
##  [8] "phenoDisco.Input"                 
##  [9] "phenoDisco.Output"                
## [10] "Curated.phenoDisco.Output"        
## [11] "SVM.marker.set"                   
## [12] "SVM.classification"               
## [13] "SVM.score"                        
## [14] "SVM.classification..top.quartile."
## [15] "Final.Localization.Assignment"    
## [16] "First.localization.evidence."     
## [17] "Curated.Organelles"               
## [18] "Cytoskeletal.Components"          
## [19] "Trafficking.Proteins"             
## [20] "Protein.Complexes"                
## [21] "Signaling.Cascades"               
## [22] "Oct4.Interactome"                 
## [23] "Nanog.Interactome"                
## [24] "Sox2.Interactome"                 
## [25] "Cell.Surface.Proteins"
\end{verbatim}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hl)[}\hlnum{1}\hlopt{:}\hlnum{3}\hlstd{]} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"uniprot.accession"}\hlstd{,} \hlstr{"uniprot.id"}\hlstd{,} \hlstr{"description"}\hlstd{)}
\hlkwd{fvarLabels}\hlstd{(hl)[}\hlnum{4}\hlopt{:}\hlnum{6}\hlstd{]} \hlkwb{<-} \hlkwd{paste0}\hlstd{(}\hlstr{"peptides.expt"}\hlstd{,} \hlnum{1}\hlopt{:}\hlnum{3}\hlstd{)}
\hlkwd{fData}\hlstd{(hl)[}\hlnum{1}\hlopt{:}\hlnum{4}\hlstd{,} \hlnum{1}\hlopt{:}\hlnum{6}\hlstd{]}
\end{alltt}
\begin{verbatim}
##          uniprot.accession  uniprot.id
## Q9JHU4              Q9JHU4 DYHC1_MOUSE
## Q9QXS1-3          Q9QXS1-3  PLEC_MOUSE
## Q9ERU9              Q9ERU9  RBP2_MOUSE
## P26039              P26039  TLN1_MOUSE
##                                                                                                                                 description
## Q9JHU4                                              Cytoplasmic dynein 1 heavy chain 1 OS=Mus musculus GN=Dync1h1 PE=1 SV=2 - [DYHC1_MOUSE]
## Q9QXS1-3 Isoform PLEC-1 of Plectin OS=Mus musculus GN=Plec - [PLEC_MOUSE]|Isoform PLEC-1A of Plectin OS=Mus musculus GN=Plec - [PLEC_MOUSE]
## Q9ERU9                                                     E3 SUMO-protein ligase RanBP2 OS=Mus musculus GN=Ranbp2 PE=1 SV=2 - [RBP2_MOUSE]
## P26039                                                                             Talin-1 OS=Mus musculus GN=Tln1 PE=1 SV=2 - [TLN1_MOUSE]
##          peptides.expt1 peptides.expt2 peptides.expt3
## Q9JHU4              175            166            322
## Q9QXS1-3            123            150            174
## Q9ERU9              101             90            181
## P26039              101             94            167
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{pData}\hlstd{(hl)}\hlopt{$}\hlstd{Replicate} \hlkwb{<-} \hlkwd{rep}\hlstd{(}\hlnum{1}\hlopt{:}\hlnum{2}\hlstd{,} \hlkwc{each} \hlstd{=} \hlnum{10}\hlstd{)}
\hlkwd{pData}\hlstd{(hl)}\hlopt{$}\hlstd{Tag} \hlkwb{<-} \hlkwd{sub}\hlstd{(}\hlstr{"\textbackslash{}\textbackslash{}.1$"}\hlstd{,} \hlstr{""}\hlstd{,} \hlkwd{sub}\hlstd{(}\hlstr{"^X"}\hlstd{,} \hlstr{""}\hlstd{,} \hlkwd{sampleNames}\hlstd{(hl)))}
\hlkwd{pData}\hlstd{(hl)}
\end{alltt}
\begin{verbatim}
##         Replicate  Tag
## X126            1  126
## X127N           1 127N
## X127C           1 127C
## X128N           1 128N
## X128C           1 128C
## X129N           1 129N
## X129C           1 129C
## X130N           1 130N
## X130C           1 130C
## X131            1  131
## X126.1          2  126
## X127N.1         2 127N
## X127C.1         2 127C
## X128N.1         2 128N
## X128C.1         2 128C
## X129N.1         2 129N
## X129C.1         2 129C
## X130N.1         2 130N
## X130C.1         2 130C
## X131.1          2  131
\end{verbatim}
\end{kframe}
\end{knitrout}
